Using pressure-driven flow systems to evaluate laser speckle contrast imaging

### 2022-06-27 article.tex
Remove unused BibTeX entries

Laser speckle contrast imaging (LSCI) is an optical imaging technique based on coherent dynamic light scattering that has been widely adopted for visualizing changes in blood flow \cite{Briers:2001hy,Boas:2010vr}. Requiring only a laser for illumination and a camera for detection, LSCI can produce full-field maps of motion with high spatiotemporal resolution. This has produced great interest in using LSCI for imaging flow in preclinical neuroscience research \cite{Ayata:2004ba,Durduran.2004,Nakamura:2010wp,He:2020} as well as a broad set of clinical applications spanning the skin \cite{Roustit.2010,Mahe.2012}, retina \cite{Briers.1982,Feng.2022}, and brain \cite{Hecht:2009gu,Parthasarathy:2010gh,Klijn:2012ls,Miller.2022}. Efforts to improve the quantitative accuracy of LSCI resulted in the development of multi-exposure speckle imaging (MESI) \cite{Parthasarathy:2008el}, which offers more robust estimates of flow compared to traditional single-exposure LSCI \cite{Parthasarathy:2010vo,Kazmi:2013hp}. The acquisition of data at multiple camera exposure times increases the dynamic range of flow sensitivity while the more comprehensive dynamic light scattering model better accounts for the presence of static scatterers and instrumentation factors. These improvements have facilitated the chronic imaging of neurovascular blood flow \cite{Schrandt:2015gu,Clark:20194vi,Williamson.2020} and offer increased sensitivity during neurosurgical measurements \cite{Richards:2017df}.

@@

The evaluation of MESI and single-exposure LSCI using the pressure-regulated flow system further demonstrates the superiority of the MESI technique \cite{Kazmi:2013hp,Sullender.2022}. The MESI estimates of relative flow outperformed LSCI at all flow speeds and closely followed the flow sensor measurements. This included the periods with no flow at the beginning and end of each experiment, where LSCI still measured relative flow of almost 0.5$\times$ the baseline. As seen in Fig. \ref{fig:error}, the \textit{largest} absolute error for MESI was comparable to that of the \textit{smallest} absolute error for LSCI. \textcolor{red}{Compare to previous measurements by Shams? Can we suggest that the slightly lower errors could be caused by using syringe pump systems?} While MESI exhibited slightly more variability during individual flow profile steps (Fig. \ref{fig:flow_mesi_lsci}a), this was probably introduced by the fitting process required to estimate $\tau_c$. This nonlinear fitting was also likely responsible for the increased error seen with MESI for flow speeds between 3.5 to 6 mm/s. \textcolor{red}{Can we actually claim this? If yes, then what exactly is happening? Is it just changes in $\rho$?} It is also possible that discrepancies between MESI and the flow sensor could be attributed to a difference in flow between the microfluidic channel and the inlet line where the flow sensor is located. Such a difference could be caused by air leakage in the inlet or outlet port of the phantom, which would reduce the flow measured by the MESI system without impacting the upstream flow measured by the flow sensor.

>>>>

Laser speckle contrast imaging (LSCI) is an optical imaging technique based on coherent dynamic light scattering that has been widely adopted for visualizing changes in blood flow \cite{Briers:2001hy,Boas:2010vr}. Requiring only a laser for illumination and a camera for detection, LSCI can produce full-field maps of motion with high spatiotemporal resolution. This has produced great interest in using LSCI for imaging flow in preclinical neuroscience research \cite{Ayata:2004ba,Durduran.2004,Nakamura:2010wp,He:2020} as well as a broad set of clinical applications spanning the skin \cite{Roustit.2010,Mahe.2012}, retina \cite{Briers.1982,Feng.2022}, and brain \cite{Hecht:2009gu,Parthasarathy:2010gh,Klijn:2012ls,Miller.2022}. Efforts to improve the quantitative accuracy of LSCI resulted in the development of multi-exposure speckle imaging (MESI) \cite{Parthasarathy:2008el}, which offers more robust estimates of flow compared to traditional single-exposure LSCI \cite{Parthasarathy:2010vo,Kazmi:2013hp}. The acquisition of data at multiple camera exposure times increases the dynamic range of flow sensitivity while the more comprehensive dynamic light scattering model better accounts for the presence of static scatterers and instrumentation factors. These improvements have facilitated the chronic imaging of neurovascular blood flow \cite{Schrandt:2015gu,Clark:20194vi,Williamson.2020,Sullender.2022} and offer increased sensitivity during neurosurgical measurements \cite{Richards:2017df}.

@@

The evaluation of MESI and single-exposure LSCI using the pressure-regulated flow system further demonstrates the superiority of the MESI technique \cite{Kazmi:2013hp}. The MESI estimates of relative flow outperformed LSCI at all flow speeds and closely followed the flow sensor measurements. This included the periods with no flow at the beginning and end of each experiment, where LSCI still measured relative flow of almost 0.5$\times$ the baseline. As seen in Fig. \ref{fig:error}, the \textit{largest} absolute error for MESI was comparable to that of the \textit{smallest} absolute error for LSCI. \textcolor{red}{Compare to previous measurements by Shams? Can we suggest that the slightly lower errors could be caused by using syringe pump systems?} While MESI exhibited slightly more variability during individual flow profile steps (Fig. \ref{fig:flow_mesi_lsci}a), this was probably introduced by the fitting process required to estimate $\tau_c$. This nonlinear fitting was also likely responsible for the increased error seen with MESI for flow speeds between 3.5 to 6 mm/s. \textcolor{red}{Can we actually claim this? If yes, then what exactly is happening? Is it just changes in $\rho$?} It is also possible that discrepancies between MESI and the flow sensor could be attributed to a difference in flow between the microfluidic channel and the inlet line where the flow sensor is located. Such a difference could be caused by air leakage in the inlet or outlet port of the phantom, which would reduce the flow measured by the MESI system without impacting the upstream flow measured by the flow sensor.
